The problem and promise of scale in multilayer animal social networks

### 2020-02-14 paper/manuscript.Rmd
add n caribou, fogo, years to all case study fig caps

<!-- Figure: metrics by social scale -->
(ref:socres) Varying scale in social threshold. For each social threshold, multilayer networks were constructed for each landcover class (forest, forage, and open) across two seasons (summer and winter) and four network metrics calculated.  A) Mean graph strength across individuals showed an increase for winter network layers at 50 m through 500 m while summer network layers had consistently weak connections. B) Mean layer relevance was relatively stable across social thresholds for each season and landcover layer. C) Similarity of landcover network layers between seasons (e.g. open summer compared to open winter) showed different responses to changing landcover scale with an overall increase in similarity for open layers and decrease in similarity for forage layers. <!--TODO: what about forest.--> D) Mean connective redundancy across individuals increased rapidly between 5 m and 50 m reaching a plateau  of about 0.65 at approximately a 50 m <!--TODO:**??**--> social threshold before decreasing between 400 m and 500 m.

@@

<!-- Figure: metrics by landcover resolution -->
(ref:lcres) Variation in multilayer network metrics as a function of changes in landcover resolution, a metric which we interpret as spatial scale. For each landcover resolution, multilayer networks were constructed for each landcover class (forest, forage, and open) across two seasons (summer and winter), and four network metrics were calculated and we examined how network metrics changed as a function of changes in spatial scale. A) Mean graph strength of individuals was weaker during the summer compared to the winter months. B) Mean layer relevance showed sparse connectivity in summer compared to winter networks and a decrease in winter forage layer relevance at higher landcover resolutions. C) Similarity of landcover network layers between seasons (e.g. open summer compared to open winter) showed different responses to changing landcover scale with an increase in similarity for forest layers at 250 m and decrease in similarity for open layers at 250 m. Note that forage layer similarity is not shown because individuals did not interact in forage habitats greater greater than 30 m landcover resolution. D) Mean connective redundancy across individuals showed a decreasing trend with increasing landcover resolution.

@@

<!-- Figure: metrics by number of observations -->
<!-- TODO: RO first sentence... -->
(ref:nobs) Varying scale in number of observations. For each iteration, a number of observations (10-485 observations in steps of 25) were selected from the complete data set to construct multilayer networks with layers defined by each landcover class (forest, forage, and open) across two seasons (summer and winter) and four network metrics calculated. A) Mean graph strength across individuals varied for winter layers becoming relatively stable at 200 observations and remained weak throughout for summer layers. B) Mean layer relevance across individuals increased for winter layers and slightly increased for summer layers. C) Similarity of landcover network layers between seasons (e.g. open summer compared to open winter) showed a stabilizing layer similarity at 200 observations for forest and 300 observations for forage and open habitats. D) Mean connective redundancy across individuals increased with increasing number of observations, which begins to plateau around 100 observations. Note, data in panel C are truncated because there were few observations of individuals in foraging and open habitats during the winter, resulting in inability to calculate layer similarity at lower number of observations.

@@

<!-- Figure: Window length -->
(ref:winlen) Varying scale in time window length. For each time window length (40 to 100 days in length increasing by 5 days in sequence), multilayer networks were constructed for each landcover class (forest, forage, and open) across two seasons (summer and winter) and four network metrics calculated. A) Mean graph strength across individuals was relatively stable over increasing time window lengths, though there was more variation in strength between landcover types as window length increased. B) Mean layer relevance generally increased during the summer months but was relatively stable across time window lengths for each landcover layer. C) Similarity of landcover network layers between seasons (e.g. open summer compared to open winter) showed increasing similarity consistent across landcover layers with increasing window length. D) Mean connective
redundancy across individuals varied dramatically depending on the length of the time window.

@@

<!-- Figure: Window position -->
(ref:winpos) Varying scale in time window position. For each time window position (shifting the start date of the time window used to define seasons 1 to 48 days from the original), multilayer networks were constructed for each landcover class (forest, forage, and open) across two seasons (summer and winter) and four network metrics calculated. A) Mean graph strength across individuals increased in summer network layers at window position 25 and increased between window position 20 and 40 for winter network layers. B) Mean layer relevance slightly decreased for winter layers and increased for summer layers, showing decreasing connectivity in shifted winter time windows and  greater connectivity in summer layers at later window positions. C) Similarity of landcover network layers between seasons (e.g. open summer compared to open winter) showed fluctuations in layer similarity across landcover types with shifted time windows. D) Mean connective redundancy across individuals increased between window position 12 through 48 due to increased connectivity in the summer network layers.

>>>>

<!-- Figure: metrics by social scale -->
(ref:socres) Varying scale in social threshold. For each social threshold, multilayer networks were constructed of caribou social associations (*Rangifer tarandus*, n = `r DT[, uniqueN(get(idcol))]`) on Fogo Island, Newfoundland in summer 2017 and winter 2018 across three habitat classes (forest, forage, and open). A) Mean graph strength across individuals showed an increase for winter network layers at 50 m through 500 m while summer network layers had consistently weak connections. B) Mean layer relevance was relatively stable across social thresholds for each season and landcover layer. C) Similarity of landcover network layers between seasons (e.g. open summer compared to open winter) showed different responses to changing landcover scale with an overall increase in similarity for open layers and decrease in similarity for forage layers. <!--TODO: what about forest.--> D) Mean connective redundancy across individuals increased rapidly between 5 m and 50 m reaching a plateau of about 0.65 at approximately a 50 m <!--TODO:**??**--> social threshold before decreasing between 400 m and 500 m.

@@

<!-- Figure: metrics by landcover resolution -->
(ref:lcres) Variation in multilayer network metrics as a function of changes in landcover resolution, a metric which we interpret as spatial scale. For each landcover resolution, multilayer networks were constructed of caribou social associations (*Rangifer tarandus*, n = `r DT[, uniqueN(get(idcol))]`) on Fogo Island, Newfoundland in summer 2017 and winter 2018 across three habitat classes (forest, forage, and open). We examined how network metrics changed as a function of changes in spatial scale. A) Mean graph strength of individuals was weaker during the summer compared to the winter months. B) Mean layer relevance showed sparse connectivity in summer compared to winter networks and a decrease in winter forage layer relevance at higher landcover resolutions. C) Similarity of landcover network layers between seasons (e.g. open summer compared to open winter) showed different responses to changing landcover scale with an increase in similarity for forest layers at 250 m and decrease in similarity for open layers at 250 m. Note that forage layer similarity is not shown because individuals did not interact in forage habitats greater greater than 30 m landcover resolution. D) Mean connective redundancy across individuals showed a decreasing trend with increasing landcover resolution.

@@

<!-- Figure: metrics by number of observations -->
<!-- TODO: RO first sentence... -->
(ref:nobs) Varying scale in number of observations. For each iteration, a number of observations (10-485 observations in steps of 25) were selected from the complete data set to construct multilayer networks of caribou social associations (*Rangifer tarandus*, n = `r DT[, uniqueN(get(idcol))]`) on Fogo Island, Newfoundland in summer 2017 and winter 2018 across three habitat classes (forest, forage, and open). A) Mean graph strength across individuals varied for winter layers becoming relatively stable at 200 observations and remained weak throughout for summer layers. B) Mean layer relevance across individuals increased for winter layers and slightly increased for summer layers. C) Similarity of landcover network layers between seasons (e.g. open summer compared to open winter) showed a stabilizing layer similarity at 200 observations for forest and 300 observations for forage and open habitats. D) Mean connective redundancy across individuals increased with increasing number of observations, which begins to plateau around 100 observations. Note, data in panel C are truncated because there were few observations of individuals in foraging and open habitats during the winter, resulting in inability to calculate layer similarity at lower number of observations.

@@

<!-- Figure: Window length -->
(ref:winlen) Varying scale in time window length. For each time window length (40 to 100 days in length increasing by 5 days in sequence), multilayer networks were constructed of caribou social associations (*Rangifer tarandus*, n = `r DT[, uniqueN(get(idcol))]`) on Fogo Island, Newfoundland in summer 2017 and winter 2018 across three habitat classes (forest, forage, and open). A) Mean graph strength across individuals was relatively stable over increasing time window lengths, though there was more variation in strength between landcover types as window length increased. B) Mean layer relevance generally increased during the summer months but was relatively stable across time window lengths for each landcover layer. C) Similarity of landcover network layers between seasons (e.g. open summer compared to open winter) showed increasing similarity consistent across landcover layers with increasing window length. D) Mean connective redundancy across individuals varied dramatically depending on the length of the time window.

@@

<!-- Figure: Window position -->
(ref:winpos) Varying scale in time window position. For each time window position (shifting the start date of the time window used to define seasons 1 to 48 days from the original), multilayer networks were constructed of caribou social associations (*Rangifer tarandus*, n = `r DT[, uniqueN(get(idcol))]`) on Fogo Island, Newfoundland in summer 2017 and winter 2018 across three habitat classes (forest, forage, and open). A) Mean graph strength across individuals increased in summer network layers at window position 25 and increased between window position 20 and 40 for winter network layers. B) Mean layer relevance slightly decreased for winter layers and increased for summer layers, showing decreasing connectivity in shifted winter time windows and  greater connectivity in summer layers at later window positions. C) Similarity of landcover network layers between seasons (e.g. open summer compared to open winter) showed fluctuations in layer similarity across landcover types with shifted time windows. D) Mean connective redundancy across individuals increased between window position 12 through 48 due to increased connectivity in the summer network layers.
